Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-02-25 tpe_edreview_rebuttal.txt

corrected, now using $\ell$ consistently for proper length.

> 8.  Suggestion: In the line above Eq. (3), if $w >> 0$ then one does
> not need absolute value bars in $|w|<< 1$.
>

Fixed, now reads "consider the proper length from $r=2M$ to
$r=2M(1+w)$ where $w$ is small, $0<w\ll 1$".

> 9.  Question.  2nd line below Eq. (4), why are radial strings
> "arbitrarily" longer than flat space would imply?  It appears the
> difference is a matter of calculation (or measurement), not arbitrary.
> Please explain this choice of words.
>

In mathematical usage (but not in general usage, at least according to
the OED) there is a disctinction in mathematics between arbitrary
arbitrarily.  One usually uses phrases like "arbitrarily large" to
convey the idea that some object may become as large as one desires.

In the manuscript the wording was "radial strings are arbitrarily
longer than flat space would imply", which I think gets the intended
meaning across.

In this case we have the astonishing result that the discrepancy
approaches infinity ("becomes arbitrarily large") as w approaches
infinity.  I have not seen this result explictly before, yet am
reluctant to claim that it is truly new: after all it is a simple
consequence of a known result (equation 3).

In any case the original wording was somewhat terse and I have
rephrased.  The sentence now reads:

> 10. Suggestion.  Line below Eq. (5), I think the word "dashes" should
> be "primes".  This is a dash: --- and this is a prime: ', at least in
> usage with which I am familiar.

### 2021-02-25 string_physics_educator_revision3.tex
fixes #36

Of course, no real string is perfectly weightless or inextensible.
With tension~$T$, gravitational acceleration $g$ and (proper) mass per
(proper) unit length~$\mu$, then a string will behave as though light
on lengthscales $L\lesssim T/\left(\mu g\right)$.  Using
$c^4/\left(4GM\right)$ for the strength of gravity at the event
horizon of a black hole with mass $M$ gives $L\lesssim TM/\left(\mu
c^4\right)$.  For the string to behave as though light on lengthscales
comparable with the Schwarzschild radius would require $T\gtrsim\mu
c^2$.  Exceeding this criterion would violate the dominant energy
condition (and in this context we note that transverse waves would
propagate at speed~$\sqrt{T/\mu}\sim c$).  Nevertheless, the
idealization of a string as light and inextensible is an interesting
and informative limit: Rindler~\cite{rindler}, for example, considers
lowering a heavy object to the event horizon on the end of such a
string to illustrate energetic arguments in GR.

>>>>

Of course, no real string is perfectly weightless or inextensible.
With tension~$T$, gravitational acceleration $g$ and (proper) mass per
(proper) unit length~$\mu$, then a string of length $\ell$ will behave
as though light if the weight of the string does not exceed the
tension, so that $T\gtrsim\ell\mu g$.  At the Schwarzschild radius
$2GM/c^2$ of a black hole with mass $M$, the Newtonian value
$g=GM/r^2$ gives $T\gtrsim\ell\mu c^4/M$.  For the string to behave as
though light on lengthscales comparable with the Schwarzschild radius
(as in the simulations below), we would require $T\gtrsim\mu c^2$.
Exceeding this criterion would violate the dominant energy condition
(and in this context we note that transverse waves would propagate at
speed~$\sqrt{T/\mu}\sim c$).  Nevertheless, the idealization of a
string as light and inextensible is an interesting and informative
limit: Rindler~\cite{rindler}, for example, considers lowering a heavy
object to the event horizon on the end of such a string to illustrate
energetic arguments in GR.
